%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Corporate Security Intern} % Job title
    {Mastercard} % Organization
    {O'Fallon, MO} % Location
    {Summer 2019} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented a web backend using \textbf{Flask} which parsed form data in order create virtual infrastructure with \textbf{Terraform}, pushed status updates to web clients with \textbf{Reddis}, and then used the \textbf{Apache Guacamole} API to allow for interaction with the newly created infrastructure over a web browser.}
        \item {Utilized ORM tool \textbf{SQLAlchemy} to store web application state data in a \textbf{PostgreSQL} database.}
        \item {Created drag-and-drop web interface using \textbf{Bootstrap} and \textbf{jQuery} which allowed for the easy deployment of over 100 virtual hacking environments in a matter of minutes.}
        \item {Collaborated with a team of interns a an educational hacking environment which demonstrated \textbf{ransomware}, Remote Access Trojans (\textbf{RATs}), and malicious Microsoft Office \textbf{macros}.}
        \item {Contributed to various web applications and \textbf{Ansible} scripts for use in the Cyber Defense Exercise, a cybersecurity competition in which several Fortune 500 companies in the finance sector compete.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Security Analyst} % Job title
    {Maryville University Cyber Fusion Center} % Organization
    {St. Louis, MO} % Location
    {Fall 2016 and Spring 2017} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Collaborated with other students to perform basic penetration testing for local charities, school districts, and small businesses using \textbf{Kali Linux} and \textbf{Nessus}}
        \item {Contributed to the writing of penetration testing reports and Standard Operating Procedures (SOPs).}
        \item {Discovered an improperly configured accounting tool on one client's website which resulted in leaked business credit card numbers.}
      \end{cvitems}
    }

%---------------------------------------------------------

  \cventry
    {Teacher's Assistance - Introduction to Computer Science} % Job title
    {LaunchCode} % Organization
    {St. Louis, MO} % Location
    {Summer 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      	\item {Assisted professor in a 10-week, fast-paced coding boot camp based on Harvard's CS50 edX course on the fundamentals of data structures and algorithms.}
        \item {Helped students learn about programming in C, Java, HTML, and JavaScript during office hours.}
        \item {Supported professor by grading assignments and answering questions in online course forum.}
      \end{cvitems}
    }

%---------------------------------------------------------
  
\end{cventries}
