%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Extracurricular Activity}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {Software Developer} % Affiliation/role
    {Multirotor Robot Student Design Team} % Organization/group
    {Rolla, MO} % Location
    {Aug. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Applied the principles of \textbf{Object-Oriented Design} to implement the core flight logic for autonomous drones in preparation for the International Aerial Robotics Competition (IARC).}
        \item {Utilized flight control framework \textbf{ArduPilot} in conjunction with the \textbf{MAVLink} protocol  \textbf{DroneKit API} to control the flight of drones with \textbf{python} code.} 
        \item {Implemented collision avoidance routine using a Scanse lidar and the python threading module.}
        \item {Evaluated flight code using the \textbf{Gazebo} robot simulation platform.}
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Website Administrator and Member} % Affiliation/role
    {ACM Coding Competition Student Organization} % Organization/group
    {Rolla, MO} % Location
    {Aug. 2018 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of experience/contributions/knowledge
        \item {Create and maintain a website using \textbf{Jekyll} and \textbf{Github Pages} to provide a convenient online location for viewing the organization's schedule of events, coding articles, and educational resources.}
        \item {Implemented a weekly-updated scoreboard which uses python to scrape the coding challenge website Kattis for the scores of each club member.}
        \item {Solved \textbf{over 180} coding challenges on Kattis in preparation for the International Collegiate Programming Competitive (ICPC).}
      \end{cvitems}
    }

%---------------------------------------------------------
\end{cventries}
